A Decision Procedure for String Constraints with String-Integer Conversion and Flat Regular Constraints

### 2021-05-10 FMCAD2021/4_dec_proc.tex
update sec 4

%\section{Quantifier Elimination Algorithm for $(\mathbb{N},+,2^x)$}
% Based on Point's work \cite{Point86}, 
We will present a revised QE algorithm for {$\paexp$} formulae of the form $Qx.\theta(x,\bar{y})$, where $Q$ is a quantifier and $\theta(x,\bar{y})$ is a quantifier-free formula. Since $\forall x. F = \neg \exists x. \neg F$, we further assume the quantifier is an existential quantifier, that is, $\exists x.\theta(x,\bar{y})$. For eliminating quantifiers in arbitrary {$\paexp$} formula, we need to apply the algorithm to the innermost quantified formula and repeat this procedure until all quantifiers are eliminated.

@@

During each iteration of the inner \emph{for} loop, if the maximal $x_i$ in $\bar{x}$ occurs in an exponential term in an atomic formula $\tau$, we will invoke \textbf{Elim-exp} to produce a new formula where $x_i$ occurs linearly equivalent to $\tau$. Then \textbf{Elim-linear} will eliminate all linear occurrences of $x_i$, which is similar to the classic Cooper's QE algorithm for PA \cite{Cooper72}.

@@

%After introducing new variables and substitution, 
After substitutions, we obtain a formula where if an exponential term contains a quantified variable $x_i$, the term must be $2^{x_i}$.
We then collect all terms with $x_i (0\le i\le n)$ together, it will be of the form $s(\bar{x}) \Def \sum_{i=0}^{n} a_i 2^{x_i} + \sum_{i=0}^n b_i x_i$, where $a_i,b_i (0\le i \le n)$ are all constants.
Other terms including constants and terms of free variables $\bar{y}$ are collected, denoted by $t(\bar{y})$. Since $\bar{y}$ are free variables, we will regard $t(\bar{y})$ as a constant. Inequalities and equalities will all be transformed into $s(\bar{x})\le t(\bar{y})$, for example, $s(\bar{x}) = t(\bar{y})$ will be replaced by $s(\bar{x})\le t(\bar{y})\wedge t(\bar{y})\le s(\bar{x})$.

At the end, the resulted formula $\theta'$ only contains literals of the forms $s(\bar{x})\le t(\bar{y})$, $k|s(\bar{x})+t(\bar{y})$ and $\neg  (k|s(\bar{x})+t(\bar{y}))$.

@@

\subsection{Enumerate-Orders} 
In the \textbf{Normalization} step, we simplify the origin formula at the cost of more quantified variables. 
Suppose we get $\exists \bar{x}.\theta(\bar{x},\bar{y})$,
and it has $n$ new variables $x_i$ ($x$ is denoted by $x_0$).
As a consequence, we need to eliminate all quantified variables one by one.

To the end, we denote the set of all orders among the $n+1$ variables by 
 $S_{n+1}$, and then enumerate these orders one by one in the outer \textit{for} loop. 
 For the considered order $\sigma$, we first add the ordering information to 
 the quantifier free formula, and then according to the 
 order, to eliminate $x_{\sigma(i)}$ for $i=n$ to $0$ by invoking \textbf{Elim-exp} first, and then invoking \textbf{Elim-linear} (the inner \textit{for} loop). 
 In each iteration of the inner \textit{for} loop, 
if $x_{\sigma{(i)}}$ occurs in an exponential term in an atomic formula, 
\textbf{Elim-exp} is invoked and a formula   equivalent to the atom is returned, in which $x_i$ occurs linearly;  
then $x_i$ occurs linearly in the formula, thus \textbf{Elim-linear} is further invoked to eliminate all occurrences of $x_i$. 
The returned formula is the disjunction of all formulas resulted in all iterations of the outer \textit{for} loop.

@@

Here is how \textbf{Elim-exp} and \textbf{Elim-linear} are invoked in
\textbf{Ordering and QE}. 
\fi

%我们这里还是考虑用循环群来做，因为如果每一次只找到最大的$x_i$，那么递归的执行还是需要整个$\bar{x}$的顺序。但如果一开始就知道了，后面有些操作可以简化

\begin{algorithm}[t]
    \SetAlgoLined
    \KwIn{a normalized $(n+1)$-existential formula $\exists \bar{x}.\theta(\bar{x},\bar{y})$,
    where $\bar{x}=(x_0,...,x_n)$} 
    \KwOut{a equivalent quantifier free formula without $\bar{x}$}

    Let $S_{n+1}$ denote the group of permutations on $\{0,1,...,n\}$\;
    $\phi :=  \textit{False}$\;
    \For{each $\sigma \in S_{n+1}$ }
    {
        $\theta_{\sigma}:=  \theta(\bar{x},\bar{y})\wedge \bigwedge_{j=0}^{n-1}(x_{\sigma(j)}\le x_{\sigma(j+1)})$\;

        \tcp{recursively eliminate the maximal $x_i$ in $\bar{x}$}
        %\znj{How to effectively determine the maximal $x_i$?} 
        \For{i from n to 0}
        {
            \tcp{if $x_{\sigma(i)}$ occurs exponentially in $\theta_\sigma$}
            $\theta_{\sigma}:= \textbf{Elim-exp}(x_{\sigma(i)},\theta_{\sigma})$\;
            \tcp{now $x_{\sigma(i)}$ occurs only linearly in $\theta_\sigma$}
            $\theta_{\sigma}:= \textbf{Elim-linear}(x_{\sigma(i)},\theta_{\sigma})$\;
        }
        $\phi :=  \phi \vee \theta_{\sigma}$\;
    }
\iffalse
    \For{i from $0$ to $n$}
    {
        \tcp{ specify the maximal quantified variable}
        $\theta_i :=  \theta(\bar{x},\bar{y}) \wedge (\bigwedge_{0\le j \le n} x_i - x_j \ge 0)$\;
        \tcp{ eliminate $x_i$}
        \While{$x_i$ occurs in an exponential term in formula $\tau(x_i,\bar{x},\bar{y})$}{
            \tcp{ Elim-exp outputs a formula equivalent with $\tau(x_i,\bar{x},\bar{y})$ where $x_i$ occurs linearly }
            $\theta_i :=  \theta_i[\text{Elim-exp}(\tau(x_i,\bar{x},\bar{y}))/\tau(x_i,\bar{x},\bar{y})]$\;
        }   
        transform $\theta_i$ into disjunction normal form $\theta_i = \bigvee_s \theta_{i,s}$\;
        \For{ every $\theta_{i,s}$ }{
            $\theta'_{i,s} :=  \text{Elim-linear}(x_i,\theta_{i,s})$
        }
        $\theta'_i =\bigvee_s \theta'_{i,s}$\;
    }
\fi
    output $\phi$
    \caption{Enumerate-Orders}
\end{algorithm}
%\znj{I cannot understand why you need to do QE for all permutation $\sigma$? I think 
%one is enough.}

@@

\textbf{Elim-exp} and \textbf{Elim-linear} are the most technical parts of our QE algorithm.
As mentioned, 
\textbf{Elim-exp} takes $\theta_{\sigma}(\bar{x},\bar{y})$ and  variable $x_{\sigma(i)}$ (the maximal variable among all quantified variables that are not eliminated yet according to $\sigma$) as 
inputs, and  outputs an equivalent formula in which $x_{\sigma(i)}$ occurs linearly.
The ideal case is that the formula $\theta(\bar{x},\bar{y})$ itself contains no $2^{x_{\sigma(i)}}$ terms, so we can omit this step and directly go to \textbf{Elim-linear}.
For simplicity, we will abuse   $x_i$ for $x_{\sigma(i)}$, 
and  $\bar{x}$ for $(x_{\sigma(0)},...,x_{\sigma(i-1)})$ ( remind that $x_{\sigma(i+1)},...,x_n$ have been eliminated already).

After normalization, the formula $\theta(\bar{x},\bar{y})$ contains atoms of three forms corresponding to 
the predicates $\le$, $|$ and negation of $|$, respectively.
The problem will be discussed in 2 cases depending on the form of the atom $\tau$ that contains $2^{x_i}$, 
corresponding to \textbf{Elim-exp-ineq} or \textbf{Elim-exp-div}.

We first give the whole procedure of \textbf{Elim-exp},
and then provide the details of the two sub-routines.
\begin{algorithm}[t]
    \SetAlgoLined
    \KwIn{$x_i$ and $\theta$, $x_i$ is larger than $x_0$ to $x_{i-1}$
    and occurs exponentially in $\theta$} 
    \KwOut{a formula equivalent to $\theta$ where $x_i$ occurs linearly}

@@

            $\quad \vee (x_i \ge \alpha +2 \wedge x_i\ge B' \wedge \bigvee_{0\le k \le \delta}(x_i = x_{i-1}+k \wedge \tau[x_{i-1}+k/x_i]))
            $\;
            \eIf{$a_i>0$}
            {
                $\Psi := \rho_1 \vee \rho_2 \vee \rho_3 \vee \rho_4 
                \vee [x_i \le \alpha -1 \wedge x_i \ge B' \wedge x_i \ge x_{i-1}+\delta]$
            }
            {
                $\Psi := \rho_1 \vee \rho_2 \vee \rho_3 \vee \rho_4 
                \vee [x_i \ge \alpha +2 \wedge x_i \ge B' \wedge x_i \ge x_{i-1}+\delta]$    
            }
            }
        {
            \tcp{ \textbf{Elim-exp-div} case, the atom is of the form $d|t(x_i,\bar{x},\bar{y})$}
            \tcp{ let $d=2^r d_0$ where $d_0$ is odd}
            $\rho_5 := \bigvee_{p=0}^{r-1} [\tau(p,\bar{x},\bar{y})\wedge x=p]$\;
            $\rho_6 := \bigvee_{q=0}^{\phi(d_0)-1} [d|(a_i 2^{r+q}+\sum_{j=0}^{i-1} a_j 2^{x_j}
            +  \sum_{k=0}^{i} b_k x_k+t(\bar{y})) \wedge \phi(d_0)|(x_i-r-q) \wedge x_i \ge r]
            $\;
            $\Psi :=  \rho_5 \vee \rho_6$
        }
        replace $\tau$ by $\Psi$ in $\theta$\;
    }
    \caption{Elim-exp}
\end{algorithm}

@@

This algorithm deals with the case where $\tau$ is an inequality of the form 
$$\tau(x_i,\bar{x},\bar{y}) \Def  a_i 2^{x_i}+\sum_{j=0}^{i-1} a_j2^{d x_j} + \sum_{k=0}^{i}b_k x_k \le t(\bar{y})$$

@@

\begin{theorem} \label{thm:exp-ineq}
Assume that $x_i$ is the maximal variable in $\bar{x}$ according to the given order. 
Given an inequality $\tau(x_i,\bar{x},\bar{y})$ of the form %, suppose $x_i$ occurs in an exponential term, that is 
$$\tau(x_i,\bar{x},\bar{y}) \Def  a_i 2^{x_i}+\sum_{j=0}^{i-1} a_j2^{d x_j} + \sum_{k=0}^{i}b_k x_k \le t(\bar{y})$$
with $a_i \neq 0$, 
let $A\Def \sum_{j=0}^{i-1}|a_j|$, 
$B\Def |b_i| + \sum_{j=0}^{i-1}|b_j|$, 
$B'\Def 2(l_2(B)+3)$,
$\delta\Def  l_2(A)+3$, then 
\begin{itemize}
    \item if $a_i > 0$, let $\alpha \Def l_2(t(y))-l_2(a_i)$
    \begin{itemize}
        \item if $x_i \le \alpha -1$, $x_i \ge B'$ and $x_{i} \ge x_{i-1} +\delta $, then $\tau(x_i,\bar{x},\bar{y})$ holds.
        \item if $x_i \ge \alpha +2$, $x_i \ge B'$ and $x_{i} \ge x_{i-1} +\delta $, then $\tau(x_i,\bar{x},\bar{y})$ \textbf{does not} hold.
    \end{itemize}
    \item if $a_i < 0$, let $\alpha \Def l_2(-t(y))-l_2(-(a_i))$
    \begin{itemize}
        \item if $x_i \le \alpha -1$, $x_i \ge B'$ and $x_{i} \ge x_{i-1} +\delta $, then $\tau(x_i,\bar{x},\bar{y})$ \textbf{does not} hold.
        \item if $x_i \ge \alpha +2$, $x_i \ge B'$ and $x_{i} \ge x_{i-1} +\delta $, then $\tau(x_i,\bar{x},\bar{y})$ holds.
    \end{itemize}
\end{itemize}
\end{theorem}

@@

Step 1: Put $\theta(x_i,\bar{x},\bar{y})$ in NNF form, replace atomic formulae containing symbols other than $\le,|$ by equivalent formulae only with $\le$, that is, $x=a$ by $x\le a \wedge a\le x$, $x< a$ by $x\le a+1$, $x\neq a$ by $x>a \vee x<a$,  $x\geq a$ by $-x \le -a$, and $x>a$ by $-x \le -a-1$.
In inequality atoms, collect terms of $x_i$
to one side and guarantee the coefficients of $x_i$ are positive.

@@

Other sub-cases are similar. However, when the abstraction parameter becomes larger,
say, $\alpha =\langle 2,2 \rangle$,
the complexity will grow rapidly,
because \textbf{Enumerate-Orders} can not always be omitted and formulae in \textbf{Elim-exp} can not be simplified easily.
\fi

>>>>

%\section{Quantifier Elimination Algorithm for $(\mathbb{N},+,2^x)$}
% Based on Point's work \cite{Point86}, 
We will present a revised QE algorithm for {$\paexp$} formulas of the form $Qx.\theta(x,\bar{y})$, where $Q$ is a quantifier and $\theta(x,\bar{y})$ is a quantifier-free formula. Since $\forall x. F = \neg \exists x. \neg F$, we further assume the quantifier is an existential quantifier, that is, $\exists x.\theta(x,\bar{y})$. For eliminating quantifiers in arbitrary {$\paexp$} formula, we need to apply the algorithm to the innermost quantified formula and repeat this procedure until all quantifiers are eliminated.

@@

During each iteration of the inner \emph{for} loop, if the maximal $x_i$ in $\bar{x}$ occurs in an exponential term in an atom, we will invoke \textbf{Elim-exp} to produce an equivalent formula where $x_i$ occurs linearly. Then \textbf{Elim-linear} will eliminate all linear occurrences of $x_i$, which is similar to the classic Cooper's QE algorithm for PA \cite{Cooper72}.

@@

%After introducing new variables and substitution, 
After substitutions, we obtain a formula where if an exponential term contains a quantified variable $x_i$, the term must be $2^{x_i}$.
We then collect all terms with $x_i (0\le i\le n)$ together, it will be of the form $s(\bar{x}) \Def \sum_{i=0}^{n} a_i 2^{x_i} + \sum_{i=0}^n b_i x_i$, where $a_i,b_i (0\le i \le n)$ are all constants.
Other terms including constants and terms of free variables $\bar{y}$ are collected, denoted by $t(\bar{y})$. Since $\bar{y}$ are free variables, we will regard $t(\bar{y})$ as a constant. Inequalities and equalities will all be transformed into $s(\bar{x})\le t(\bar{y})$, for example, $s(\bar{x}) = t(\bar{y})$ will be replaced by $s(\bar{x})\le t(\bar{y})\wedge t(\bar{y})\le s(\bar{x})$.
 end, the resulted formula $\theta'$ only contains literals of the forms $s(\bar{x})\le t(\bar{y})$, $k|s(\bar{x})+t(\bar{y})$ and $\neg  (k|s(\bar{x})+t(\bar{y}))$.

@@

\subsection{Enumerate-Orders} 
In the \textbf{Normalization} step, we simplify the origin formula at the cost of more quantified variables. Suppose we get $\exists \bar{x}.\theta(\bar{x},\bar{y})$ and it has $n$ new variables $x_i$. As a consequence, we need to eliminate all $(n+1)$ quantified variables one by one.

%To the end, 
We denote the set of all orders among the $(n+1)$ variables by $S_{n+1}$, and then enumerate these orders one by one in the outer \textit{for} loop. For the considered order $\sigma$, we first add the ordering information to $\theta$, and then according to the order, to eliminate $x_{\sigma(i)}$ for $i=n$ to $0$ by invoking \textbf{Elim-exp} first, and then invoking \textbf{Elim-linear} (the inner \textit{for} loop). In each iteration of the inner \textit{for} loop, if $x_{\sigma{(i)}}$ occurs in an exponential term in an atom $\tau$, \textbf{Elim-exp} is invoked to produce a formula, in which $x_i$ occurs linearly, equivalent to $\theta$;  
then $x_i$ occurs only linearly, thus \textbf{Elim-linear} is further invoked to eliminate all (linear) occurrences of $x_i$. The returned formula is the disjunction of all formulas resulted in all iterations of the outer \textit{for} loop.

@@

Here is how \textbf{Elim-exp} and \textbf{Elim-linear} are invoked in
\textb
At thef{Ordering and QE}. 
\fi

\begin{algorithm}[t]
    \SetAlgoLined
    \KwIn{a normalized $(n+1)$-existential formula $\exists \bar{x}.\theta(\bar{x},\bar{y})$, where $\bar{x}=(x_0,...,x_n)$} 
    \KwOut{an equivalent quantifier-free formula without $\bar{x}$}
    \tcp{Let $S_{n+1}$ denote the group of permutations on $\{0,1,...,n\}$}
    $\phi := \textit{False}$\;
    \For{each $\sigma \in S_{n+1}$ }
    {
        $\theta_{\sigma}:=  \theta(\bar{x},\bar{y})\wedge \bigwedge_{j=0}^{n-1}(x_{\sigma(j)}\le x_{\sigma(j+1)})$\;

        \tcp{recursively eliminate the maximal $x_i$ in $\bar{x}$}
        %\znj{How to effectively determine the maximal $x_i$?} 
        \For{i from n to 0}
        {
            \tcp{if $x_{\sigma(i)}$ occurs exponentially in $\theta_\sigma$}
            $\theta_{\sigma}:= \textbf{Elim-exp}(x_{\sigma(i)},\theta_{\sigma})$\;
            \tcp{now $x_{\sigma(i)}$ occurs only linearly in $\theta_\sigma$}
            $\theta_{\sigma}:= \textbf{Elim-linear}(x_{\sigma(i)},\theta_{\sigma})$\;
        }
        $\phi :=  \phi \vee \theta_{\sigma}$\;
    }
    output $\phi$
    \caption{Enumerate-Orders}
\end{algorithm}

@@

\textbf{Elim-exp} is the most technical part of our QE algorithm. As mentioned, \textbf{Elim-exp} takes $\theta_{\sigma}(\bar{x},\bar{y})$ and  variable $x_{\sigma(i)}$ (the maximal variable among all quantified variables that are not eliminated yet according to $\sigma$) as inputs, and outputs an equivalent formula in which $x_{\sigma(i)}$ occurs linearly.
The ideal case is that the formula $\theta(\bar{x},\bar{y})$ itself contains no $2^{x_{\sigma(i)}}$ terms, so we can omit this step and directly go to \textbf{Elim-linear}.
For simplicity, we will abuse notations $x_i$ for $x_{\sigma(i)}$, and $\bar{x}$ for $(x_{\sigma(0)},...,x_{\sigma(i-1)})$ ( remind that $x_{\sigma(i+1)},...,x_n$ have been eliminated already).

After normalization, the formula $\theta(\bar{x},\bar{y})$ contains atoms of three forms corresponding to 
the predicates $\le$, $|$ and negation of $|$, respectively.
The problem will be discussed in two cases depending on the form of the atom $\tau$ that contains $2^{x_i}$, 
corresponding to \textbf{Elim-exp-ineq} or \textbf{Elim-exp-div}.

%We first give the whole procedure of \textbf{Elim-exp},and then provide the details of the two sub-routines.

\begin{algorithm}[t]
    \SetAlgoLined
    \KwIn{$x_i$ and $\theta$, $x_i$ is larger than $x_0$ to $x_{i-1}$
    and occurs exponentially in $\theta$} 
    \KwOut{a formula equivalent to $\theta$ where $x_i$ occurs linearly}

@@

            $\quad \vee (x_i \ge \alpha +2 \wedge x_i\ge B' \wedge \bigvee_{0\le k \le \delta}(x_i = x_{i-1}+k \wedge \tau[x_{i-1}+k/x_i]))
            $\;
            \eIf{$a_i>0$}
            {
                $\Psi := \rho_1 \vee \rho_2 \vee \rho_3 \vee \rho_4 
                \vee [x_i \le \alpha -1 \wedge x_i \ge B' \wedge x_i \ge x_{i-1}+\delta]$
            }
            {
                $\Psi := \rho_1 \vee \rho_2 \vee \rho_3 \vee \rho_4 
                \vee [x_i \ge \alpha +2 \wedge x_i \ge B' \wedge x_i \ge x_{i-1}+\delta]$    
            }
            }
        {
            \tcp{the atom is of the form $d|t(x_i,\bar{x},\bar{y})$}
            \tcp{ \textbf{Elim-exp-div} case}
            \tcp{ let $d=2^r d_0$ where $d_0$ is odd}
            $\rho_5 := \bigvee_{p=0}^{r-1} [\tau(p,\bar{x},\bar{y})\wedge x=p]$\;
            $\rho_6 := \bigvee_{q=0}^{\phi(d_0)-1} [d|(a_i 2^{r+q}+\sum_{j=0}^{i-1} a_j 2^{x_j}
            +  \sum_{k=0}^{i} b_k x_k+t(\bar{y})) \wedge \phi(d_0)|(x_i-r-q) \wedge x_i \ge r]
            $\;
            $\Psi :=  \rho_5 \vee \rho_6$
        }
        replace $\tau$ by $\Psi$ in $\theta$\;
    }
    \caption{Elim-exp}
\end{algorithm}

@@

This part deals with the case when $\tau$ is an inequality of the form 
$$\tau(x_i,\bar{x},\bar{y}) \Def  a_i 2^{x_i}+\sum_{j=0}^{i-1} a_j2^{d x_j} + \sum_{k=0}^{i}b_k x_k \le t(\bar{y})$$

@@

\begin{theorem} \label{thm:exp-ineq}
Assume that $x_i$ is the maximal variable in $\{x_0,...,x_{i}\}$ according to the given order, $\bar{x}$ denotes $\{x_0,...,x_{i-1}\}$.
Given an inequality $\tau(x_i,\bar{x},\bar{y})$ of the form  
$$\tau(x_i,\bar{x},\bar{y}) \Def  a_i 2^{x_i}+\sum_{j=0}^{i-1} a_j2^{d x_j} + \sum_{k=0}^{i}b_k x_k \le t(\bar{y})$$
with $a_i \neq 0$. Define $A\Def \sum_{j=0}^{i-1}|a_j|$, 
$B\Def |b_i| + \sum_{j=0}^{i-1}|b_j|$, 
$B'\Def 2(l_2(B)+3)$,
$\delta\Def  l_2(A)+3$, then 
\begin{itemize}
    \item if $a_i > 0$, let $\alpha \Def l_2(t(y))-l_2(a_i)$
    \begin{itemize}
        \item if $x_i \le \alpha -1$, $x_i \ge B'$ and $x_{i} \ge x_{i-1} +\delta $, then $\tau(x_i,\bar{x},\bar{y})$ holds.
        \item if $x_i \ge \alpha +2$, $x_i \ge B'$ and $x_{i} \ge x_{i-1} +\delta $, then $\tau(x_i,\bar{x},\bar{y})$ \textbf{does not} hold.
    \end{itemize}
    \item if $a_i < 0$, let $\alpha \Def l_2(-t(y))-l_2(-(a_i))$
    \begin{itemize}
        \item if $x_i \le \alpha -1$, $x_i \ge B'$ and $x_{i} \ge x_{i-1} +\delta $, then $\tau(x_i,\bar{x},\bar{y})$ \textbf{does not} hold.
        \item if $x_i \ge \alpha +2$, $x_i \ge B'$ and $x_{i} \ge x_{i-1} +\delta $, then $\tau(x_i,\bar{x},\bar{y})$ holds.
    \end{itemize}
\end{itemize}
\end{theorem}

@@

Step 1: Put $\theta(x_i,\bar{x},\bar{y})$ in NNF form, replace atomic formulas containing symbols other than $\le,|$ by equivalent formulas only with $\le$, that is, $x=a$ by $x\le a \wedge a\le x$, $x< a$ by $x\le a+1$, $x\neq a$ by $x>a \vee x<a$,  $x\geq a$ by $-x \le -a$, and $x>a$ by $-x \le -a-1$.
In inequality atoms, collect terms of $x_i$
to one side and guarantee the coefficients of $x_i$ are positive.

@@

Other sub-cases are similar. However, when the abstraction parameter becomes larger,
say, $\alpha =\langle 2,2 \rangle$,
the complexity will grow rapidly,
because \textbf{Enumerate-Orders} can not always be omitted and formulas in \textbf{Elim-exp} can not be simplified easily.
\fi
